---
title: "A1_Green_20158921"
author: "Alyssa Green"
date: "2023-01-11"
output: html_document
---
[Link to GitHub Repository](https://github.com/alyssagreen02/BIOL432_Assignment1)

### Load libraries
```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)
library(tidyr)
source("http://bit.ly/theme_pub")
```

### Load previous R scripts
##### Load script that generates limb measurement data
```{r}
source("dataGenerato.R")
```

##### Load script that calculates limb volume data
```{r}
source("volumeEstimato.R")
```

### Load measurements.csv
```{r}
measurements=read.csv("measurements.csv")
```

### Sort data by species, then by observer, then by limb volume
```{r}
measurements=measurements%>%arrange(Organism, Observer, Volume)
measurements
```

### Generate table showing average volume for each species
```{r}
AvgVol=measurements%>%group_by(Organism)%>%summarise(Average_Volume=mean(Volume))
AvgVol
```

### Generate table showing number of observations for each combination of species and observer
```{r}
Num_Obs=measurements%>%count(Organism, Observer)
Num_Obs
```

### Create boxplot to compare key features of the distributions of volumes for each species
```{r}
ggplot(data = measurements, aes(x=Organism, y=Volume))+geom_boxplot()+theme_pub()
```

### Generate multi-panel plot showing frequency histograms for each species
```{r}
SP=measurements%>%filter(Organism=="Specious peoples")
GB=measurements%>%filter(Organism=="Grenous benous")
PE=measurements%>%filter(Organism=="Purlous elefanous")
PG=measurements%>%filter(Organism=="Pinkus grafiarous")
OS=measurements%>%filter(Organism=="Orng samples")


SPP=ggplot(aes(Volume), data=SP)+geom_bar()+theme_pub()+ggtitle("Specious peoples")
GBP=ggplot(aes(Volume), data=GB)+geom_bar()+theme_pub()+ggtitle("Grenous benous")
PEP=ggplot(aes(Volume), data=PE)+geom_bar()+theme_pub()+ggtitle("Purlous elefanous")
PGP=ggplot(aes(Volume), data=PG)+geom_bar()+theme_pub()+ggtitle("Pinkus grafiarous")
OSP=ggplot(aes(Volume), data=OS)+geom_bar()+theme_pub()+ggtitle("Orng samples")

grid.arrange(SPP, GBP, PEP, PGP, OSP ,ncol=2)
```

